Bone-Conduction and Spatialised Audio to Guide People with Visual Impairments

### 2019-07-15 paper.tex
Changes to figures, added new signed error figure

The data collected during the experiment were grouped together by participant group and analysed.
Similar to the results from~\cite{macdonald2006spatial,schonstein2008comparison}, we use the absolute mean errors for each dimension which allows us to compare our results to the aforementioned works'. 
These results are presented in the boxplots in \cref{fig:err-results} and summarised in \cref{tab:results}.

\begin{figure}[t]
  \centering
  \includegraphics[width=0.7\columnwidth]{figures/pan_tilt_err.png}
  \caption{Boxplots of the angular errors collected during the pointing experiment. }\label{fig:err-results}
\end{figure}

\begin{table}
  \centering
  \caption{A summary of the results collected from the experiment. }\label{tab:results}
  \begin{tabular}{p{1cm}p{2cm}p{2.2cm}@{\hskip 1cm}p{3cm}}
    \toprule
    &           & Mean absolute error [rad]  & Spearman Correlation score \\ \midrule
    \multirow{2}{*}{\textit{G1}} & Pan       & $0.23\pm0.24$ & $0.88\;(p<0.001)$ \\
				 & Elevation & $0.25\pm0.28$ & $0.64\;(p<0.001)$ \\ \midrule
    \multirow{2}{*}{\textit{G2}} & Pan       & $0.45\pm0.21$ & $0.41\;(p<0.001)$ \\
				 & Elevation & $0.36\pm0.32$ & $0.61\;(p=0.001)$ \\
    \bottomrule
  \end{tabular}
\end{table}

@@

The elevation estimation performance for both groups deteriorated when compared to their pan estimation results, which was somewhat expected given previous research results on human audition~\cite{barfield1997visual}. 
The mean absolute errors of the participants are \SI{0.25}{\radian} and \SI{0.36}{\radian} for groups \textit{G1} and \textit{G2} respectively.
As with the pan estimation errors, the participants from \textit{G1} seemed more adept at estimating the correct elevation.
%However, the difference is not as significant as for the pan, with \textit{G1} displaying a 36\% improvement over \textit{G2} in their elevation estimation vs. 42.5\% in the pan dimension. 
Comparing these results to methods that convey elevation through an HRTF, we see an improvement of approximately 63\% and 47\% for each group~\cite{schonstein2008comparison}. 
Indeed, the performance is comparable to that of open-back and expensive in-ear headphones.
There is a more modest improvement of 43\% in \textit{G1} and 16\% for \textit{G2} when compared to the individualised and adjusted HRTFs in~\cite{stanley2006lateralization}.
However, the participants from~\cite{stanley2006lateralization} all had healthy eyesight, making the latter comparison invalid. 
Interestingly, the elevation errors for group \textit{G2} are centred around the negative angle, indicating a possible underlying bias in the participants or the interface\todo{show}.
A similar trend was observed in~\cite{stanley2006lateralization} and warrants an investigation with a larger participant pool to determine the underlying bias, if any.

>>>>

The data collected during the experiment were grouped together by participant group and analysed.
Similar to the results from~\cite{macdonald2006spatial,schonstein2008comparison}, we use the absolute mean errors for each dimension which allows us to compare our results to the aforementioned works'. 
These results are presented in the boxplots in \cref{fig:err-results-fig} and summarised in \cref{tab:results}.

\begin{figure}
  \centering
  \subfloat[]{\label{fig:err-results-abs}\includegraphics[width=0.7\columnwidth]{figures/pan_tilt_err_abs.png}}
\quad
  \subfloat[]{\label{fig:err-results}\includegraphics[width=0.7\columnwidth]{figures/pan_tilt_err.png}}
  \caption{Boxplots of the absolute (top) and signed (bottom) angular errors collected during the pointing experiment. }\label{fig:err-results-fig}
\end{figure}

\begin{table}
  \centering
  \caption{A summary of the results collected from the experiment. }\label{tab:results}
  \begin{tabular}{p{1cm}p{2cm}p{2.2cm}@{\hskip 1cm}p{3.2cm}}
    \toprule
    &           & Mean absolute error [rad]  & Spearman Correlation score \\ \midrule
    \multirow{2}{*}{\textit{G1}} & Pan       & $0.23\pm0.24$ & $0.88\;(p<0.001)$ \\
				 & Elevation & $0.25\pm0.28$ & $0.64\;(p<0.001)$ \\ \midrule
    \multirow{2}{*}{\textit{G2}} & Pan       & $0.45\pm0.21$ & $0.41\;(p<0.001)$ \\
				 & Elevation & $0.36\pm0.32$ & $0.61\;(p<0.001)$ \\
    \bottomrule
  \end{tabular}
\end{table}

@@

The elevation estimation performance for both groups deteriorated when compared to their pan estimation results, which was somewhat expected given previous research results on human audition~\cite{barfield1997visual}. 
The mean absolute errors of the participants are \SI{0.25}{\radian} and \SI{0.36}{\radian} for groups \textit{G1} and \textit{G2} respectively.
As with the pan estimation errors, the participants from \textit{G1} seemed more adept at estimating the correct elevation.
%However, the difference is not as significant as for the pan, with \textit{G1} displaying a 36\% improvement over \textit{G2} in their elevation estimation vs. 42.5\% in the pan dimension. 
Comparing these results to methods that convey elevation through an HRTF, we see an improvement of approximately 63\% and 47\% for each group~\cite{schonstein2008comparison}. 
Indeed, the performance is comparable to that of open-back and expensive in-ear headphones.
There is a more modest improvement of 43\% in \textit{G1} and 16\% for \textit{G2} when compared to the individualised and adjusted HRTFs in~\cite{stanley2006lateralization}.
However, the participants from~\cite{stanley2006lateralization} all had healthy eyesight, making the latter comparison invalid. 
Interestingly, the elevation errors for group \textit{G2} are centred around the negative angle, as seen in \cref{fig:err-results}, indicating a possible underlying bias in the participants or the interface.
A similar trend was observed in~\cite{stanley2006lateralization} and warrants an investigation with a larger participant pool to determine the underlying bias, if any.
